---
title: "Session 2: Looking at the SHHS data"
output: html_notebook
---

Welcome to your first R Notebook! This is a way to start executing R Code. We're going to step through an introductory exploration of our dataset. 

The grey block below is a *code block*. Try pressing the green play button on the top right. What do you think is going to happen?

```{r}
3 + 10 
```

We're going to start looking at the Sleep Health Heart Study (SHHS) Data. To do so, we first need to 

1) load some software packages to help us explore the data (using the `library()` command), and 
2) load the data and data dictionary (using `readRDS()`, which reads in R's internal data format and `read.csv()`, which reads in a Comma-Separated-Value (`csv`) file.

Execute this code block.

```{r}
library(here)
library(burro)

sleep_data <- readRDS(here("data/common_data_small.rds"))
data_dictionary <- read.csv(here("data/shhs-data-dictionary-0.13.1-variables.csv"))
```

# Looking at the tabular form of the data

Our data is loaded as a table (also known as a `data.frame`) into R. A useful command to look at the data in its tabular form is `View()`. Try it out by running the code block below. Another window should pop up and you should see an Excel-like table. 

```{r}
View(sleep_data)
```

# What are our variables and what do they mean?



# Running `burro` on our dataset

Now we can start looking at the data in a more summarized format. Try running the code chunk below to open up `burro`, which is a data explorer that we're going to use to ask questions. We know our outcome variable is.

When you want to continue on in the notebook, be sure to hit the red stop button on the top right of the code block.

```{r}
burro::explore_data(dataset= sleep_data, 
             outcome_var = "any_cvd", 
             data_dictionary = data_dictionary)
```

# Some Questions for the Overview Panel (5-10 minutes)

As a group, take a look at the following questions and attempt to answer them from the overview panel. 

As you do, take a note of which tab (`Visual Summary`, `Tabular Summary`, and `Data Dictionary`) you found the information in.

Be sure to use your post-it notes if you're confused or need help!

1.How many categorical variables (also called `factor`s) are there in our dataset?
2.How many Missing Cardiovascular Disease Cases are there?
3. What is the mean age for the dataset? Is it what you expected?
4. How is the `oahi` variable calculated?

```{r}

```

# The Category Panel

# Some Questions for the Category Panel (5-10 minutes)

