---
title: "Welcome to Clinical Data Wrangling"
author: "Eilis Boudreau, Nicole Weiskopf, Ted Laderas and Aaron Coyner"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
duo_accent(
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
)
```

# Goals of this workshop

1. Understand the benefits and drawbacks of working with electronic health record (EHR) data.
2. Learn basic competencies in clinical data wrangling with a realistic clinical dataset.
3. Learn basic competencies in exploratory data analysis (EDA) in order to identify issues in EHR data.

---
# About Us

- Intros

---

# Code of Conduct

Please read the Code of Conduct. We want to foster a positive learning environment. 

- Respect how each other learns
- Help each other learn
- Don't belittle each other

---

# Protected Health Information

- Remember, this dataset is considered Protected Health Information.
- Don't share the data with anyone.

---
# Today's Schedule

- 9:00 - 9:15 These Slides
- 9:15 – 9:55 Session 1a: Learning about Sleep Data and clinical data
- 9:55 - 10:15 Session 1b: The Value of Clinical Data
- 10:15 – 10:30 Break
- 10:30 – 12 Session 2a: Exploring the Dataset with `burro`
- 12:00 - 1:00 PM: Lunch Break (on your own)
- 1:00 PM – 2:00 PM Session 2b: Understanding the Data
- 2:00 - 2:15 Break
- 2:15 – 4:00 Session 3: Starting to build a predictive model with the
R Notebook
- 4:00-4:30 Discussion of Day 1/Wrap up

---
# Future Sessions

- Day 2 (Tuesday), Session 4: 1-2 PM KCRB 1000
    - Q & A about modeling
    - Discussion about `race` as a variable
- Day 3 (Wednesday), Session 5: 2:00-5:00 PM KCRB 1000
    - Discussion about hypertension
    - Work on Final Presentation 
- Day 4 (Thursday), Session 6: 3:30-5:30 BICC 124
    - Final Presentation about Data
---

## It's Dangerous to Learn Alone

Pair up together and get to know each other:

- Your Name
- What do you want to learn from this workshop?
- Would you rather be a Pirate or Ninja? Why?

---

## The Post It System

Remember, the first line of defense is your team.

- Red - I need help!
- Yellow - Things are peachy-keen/I'm done with what you asked
