---
title: "Welcome to Clinical Data Wrangling"
author: "Eilis Boudreau, Nicole Weiskopf, Ted Laderas and Aaron Coyner"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
mono_dark(
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
)
```

# Goals of this workshop

1. Understand the benefits and drawbacks of working with electronic health record (EHR) data.
2. Learn basic competencies in clinical data wrangling with a realistic clinical dataset.
3. Learn basic competencies in exploratory data analysis (EDA) in order to identify issues in EHR data.

---

# About Us

- Intros

---

# Code of Conduct

Please read the Code of Conduct. We want to foster a positive learning environment. 

- Respect how each other learns
- Help each other learn
- Don't belittle each other

---

# Protected Health Information

- Remember, this dataset is considered Protected Health Information.
- Don't share the data with anyone.

---
# Today's Schedule

- 9:00 - 9:30 These Slides
- 9:30 – 10:15 Session 1: Learning about Sleep Data and clinical data
- 10:15 – 10:30 Break
- 10:30 – 12 Session 2a: Exploring the Dataset with `burro`
- 12:00 - 1:00 PM: Lunch Break (on your own)
- 1:00 PM – 2:30 Session 2b: Understanding the Data
- 2:30-2:45 Break
- 2:45 – 4:00 Session 3: Starting to build a predictive model with the
R Notebook
- 4:00-4:30 Discussion of Day 1/Wrap up

---
# Future Sessions

- Day 2 (Tuesday), Session 4: 1-2 PM KCRB 1000
- Day 3 (Wednesday), Session 5: 2:30-5 PM KCRB 1000
- Day 4 (Thursday), Session 6: 3:30-5:30 BICC 124
- Times/topics subject to change

---

## It's Dangerous to Learn Alone

Pair up together and get to know each other:

- What is your major?
- What do you want to learn?

---

## The Post It System

Remember, the first line of defense is your team.

- Red - I need help!
- Green - Things are peachy-keen/I'm done with what you asked
