---
title: "How to Make the EDA Visualizations"
author: "Ted Laderas"
date: "9/20/2018"
output: 
  html_document:
    toc: true
    toc_float: true
---

This is a small document showing you how I constructed each of the visualizations for the EDA Shiny App.

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(visdat)
library(ggplot2)
library(dplyr)
library(skimr)
library(naniar)

shhs_data <- readRDS(here("data/common_data_small.rds"))
```

## Visdat Overview of the Data

```{r}
shhs_data %>% visdat::vis_dat()
```

## Skimr Overview of the Data

```{r}
skimr::skim(shhs_data)
```

## Categorical: Barplot of a single variable

```{r}
shhs_data %>% ggplot(aes(x=any_cvd, fill=any_cvd)) + geom_bar()
```

## Categorical: Proportional Plot of `race` vs `any_cvd`

```{r}
shhs_data %>% ggplot(aes(x=race, fill=any_cvd)) + geom_bar(position = "fill")
```

## Categorical: Missing Value Plot of `any_cvd` versus all other variables

```{r}
shhs_data %>% naniar::gg_miss_fct(fct = any_cvd)
```

## Continuous: Histogram of `age_s1`

```{r}
shhs_data %>% ggplot(aes(x=age_s1)) + geom_histogram(bins = 40)
```

## Continuous: Boxplot of `age_s1` versus `race`

```{r}
shhs_data %>% ggplot(aes(x=race, y= age_s1, fill=race)) + geom_boxplot()
```

## Continous: Scatterplot of `bmi_s1` versus `neck20`

```{r}
shhs_data %>% ggplot(aes(x=bmi_s1, y=neck20)) + geom_point() + stat_smooth(method="lm", se=FALSE)
```

## Continous: Scatterplot of `bmi_s1` versus `neck20` with missing data

```{r}
shhs_data %>% ggplot(aes(x=bmi_s1, y=neck20)) + naniar::geom_miss_point() + stat_smooth(method="lm", se=FALSE)
```